Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-11 paper.qmd
Figurw 15 check with the scale factors

## First projection
projection <- cbind(
    c(0.71503,0.00502,-0.04370,-0.01811,-0.01103,0.09877,0.06199,0.05396,0.07771,-0.01713),
    c(0.00587,0.71879,0.03485,0.08284,-0.07534,-0.05420,0.04315,-0.00547,-0.02995,0.01810))

@@

mnist_proj_tsne_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    size = 0.2,
    alpha = 0.2) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-1, 1)) +
  ylim(c(-1, 1)) +
  interior_annotation("b")

## Second projection
projection <- cbind(
    c(-0.33305,0.20223,0.06303,0.11124,0.13299,-0.30093,0.34082,0.15581,-0.08864,0.33573),
    c(0.53615,0.14969,-0.09393,-0.20053,0.07992,-0.34791,0.13057,-0.06814,-0.16737,0.03716))

@@

## Third projection
projection <- cbind(
    c(-0.12783,-0.50063,-0.02631,-0.00484,0.17733,0.37157,0.11310,0.09424,0.19844,0.19792),
    c(-0.42542,0.29570,0.31106,-0.30307,0.00614,0.16714,0.21779,-0.00025,0.07020,-0.00689))

>>>>

## First projection
projection <- cbind(
    c(0.71503,0.00502,-0.04370,-0.01811,-0.01103,0.09877,0.06199,0.05396,0.07771,-0.01713),
    c(0.00587,0.71879,0.03485,0.08284,-0.07534,-0.05420,0.04315,-0.00547,-0.02995,0.01810)) * 1.3

@@

mnist_proj_tsne_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    size = 0.2,
    alpha = 0.2) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  #coord_fixed() +
  xlim(c(-1, 1)) +
  ylim(c(-1, 1)) +
  interior_annotation("b")

## Second projection
projection <- cbind(
    c(-0.33305,0.20223,0.06303,0.11124,0.13299,-0.30093,0.34082,0.15581,-0.08864,0.33573),
    c(0.53615,0.14969,-0.09393,-0.20053,0.07992,-0.34791,0.13057,-0.06814,-0.16737,0.03716)) * 2

@@

## Third projection
projection <- cbind(
    c(-0.12783,-0.50063,-0.02631,-0.00484,0.17733,0.37157,0.11310,0.09424,0.19844,0.19792),
    c(-0.42542,0.29570,0.31106,-0.30307,0.00614,0.16714,0.21779,-0.00025,0.07020,-0.00689)) * 1.5
